A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-16 doc/sigchi14/targeting.tex
modified targeting
fixed CT attributions

\subsection{Participants}
We recruited 15 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance \claire as the glasses beneath Glass make it more cumbersome to secure the position of the Glass and to adjust the screen to the optimal angle.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/selection-times2.pdf}
\caption{Task completion times. \bjoern{update data}}
\label{fig:selection-times}
\end{figure}
\subsection{Results}

\subsubsection{Performance data}
The time to complete each task can be broken down into the following pieces:

@@

@@

\claire One noted benefit of IR mode was a feeling that it was \studyquote{more direct}. One subject appreciated the ability to \studyquote{interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

\claire A perceived shortcoming of IR mode was the necessity to move the head in order to control a device. One participant said that it was \studyquote{awkward to be aiming your head at things, tweaking back and forth to get it right}. Another noted that observing the head movement didn't capture the site of her attention, because \studyquote {eye movement is an important part of how people look around}.

>>>>

\subsection{Participants}
We recruited 15 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance \claire{ as the glasses beneath Glass make it more cumbersome to secure the position of the Glass and to adjust the screen to the optimal angle.}

@@

\subsection{Results}
\subsubsection{Performance data}
The time to complete each task can be broken down into the following pieces:

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/R_time_by_Category.pdf}
\caption{Task completion times.} \sean{label mean on the chart}
\label{fig:selection-times}
\end{figure}

As a result, infrared mode out performs list mode by 2.186 seconds (6.672 vs 8.858), as shown in figure~\ref{fig:selection-times}. \sean{TBC}

@@

\claire{ One noted benefit of IR mode was a feeling that it was \studyquote{more direct}. One subject appreciated the ability to \studyquote{interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

 A perceived shortcoming of IR mode was the necessity to move the head in order to control a device. One participant said that it was \studyquote{awkward to be aiming your head at things, tweaking back and forth to get it right}. Another noted that observing the head movement didn't capture the site of her attention, because \studyquote {eye movement is an important part of how people look around}.}
